---
title: "esm205_lab10xxx"
author: "Sachiko Lamen"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(usethis)
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```

## beepr::beep() 
This function beeps when your code is done running
Use `beep()` to give yourself an audio alert.

## Write a for loop + beep

```{r, eval = FALSE}
# create sequence from 1-99 but wrap in reverse function so that you can count backwards. For each element `i` reverse the sequence from 1 to 99
for(i in rev(seq(1:100)))(
  print(paste(i, "bottles of beer on the wall"))
)

beep(9)
```

## praise is nice
provides you with a nice message out of the box

```{r}
# can specify a template for how you want the phrase to look
praise("${EXCLAMATION}!!! This code works ${adverb_manner}!")

praise("Holy ${exclamation}, you are ${adjective}")
```

## cowsay:: say to have characters say something
```{r}
say("Im tripping ballz!", by = "rms")
```

## usethis for everything

R Project first, then git & Github repo.
To save into version control if you did not set up in version control

- usethis::use_git()
- usethis::use_github()





