---
title: "esm205_lab10xxx"
author: "Sachiko Lamen"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(usethis)
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```

## beepr::beep() 
This function beeps when your code is done running
Use `beep()` to give yourself an audio alert.

## Write a for loop + beep

```{r, eval = FALSE}
# create sequence from 1-99 but wrap in reverse function so that you can count backwards. For each element `i` reverse the sequence from 1 to 99
for(i in rev(seq(1:100)))(
  print(paste(i, "bottles of beer on the wall"))
)

beep(9)
```

## praise is nice
provides you with a nice message out of the box

```{r}
# can specify a template for how you want the phrase to look
praise("${EXCLAMATION}!!! This code works ${adverb_manner}!")

praise("Holy ${exclamation}, you are ${adjective}")
```

## cowsay:: say to have characters say something
```{r}
say("Im tripping ballz!", by = "rms")
```

## usethis for everything ALSO CONVERT TO VERSION CONTROL***

R Project first, then git & Github repo.
To save into version control if you did not set up in version control

- usethis::use_git()
- usethis::use_github()

## paletteer: aggregated color palettes

```{r}
storms %>% 
  group_by(name) %>%
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>%
  slice_min(n = 10, min_pressure) %>%# find minimum 10 values 
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("basetheme::brutal")

# type paletteer_d("basetheme::brutal") into console to see hexadecimal color code

```

## Map of Jornada LTER Vegetation
use `read_sf()` to read in NON csv file
```{r}
jornada_veg <- read_sf("doc.kml") %>%
  select(Name) %>%
  clean_names()

# create a map of vegetation types using ggplot
ggplot() +
  geom_sf(data = jornada_veg)

# Update this map: 
# each vegetation type has a different ill color
# update the theme
# customize the color pallete

ggplot(data = jornada_veg) +
  geom_sf(aes(fill = name), color = NA) + # (aes(fill = name) fill different names with different colors, (color = NA) remove barrier lines
  scale_fill_paletteer_d("vapeplot::vaporwave") +
  theme_minimal() +
  labs(title = "Jornada Basin LTER Vegetation")

# use ggsave to automatically store the MOST RECENTLY GENERATED plot

ggsave(filename = "my_awesome_jornada_map.png", width = 8, height = 5)
```

